---
title: "Project PTDS"
author: "Luca Bron, David Germano, Patrik Grandadam, Vincent Lomazzi, Edgar Raisin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    theme: cerulean
    highlight: tango
---

```{r message=FALSE, warning=FALSE}
library(robotstxt)
library(xml2)
library(rvest)
library(magrittr)
library(stringr)
library(dplyr)
library(plotly)
library(ggmap)
library(googleway)
library(leaflet)
```


# Webscrapping

Example data structure de Iegor a rearranger

```{r}
cities <- list(
  zurich = list(),
  geneve = list(),
  basel = list(),
  lausanne = list(),
  bern = list(),
  winterthur = list(),
  lucerne = list(),
  lugano = list()
  )
```


## Immoscout

Is the path allowed for each city? 

```{r, eval = FALSE}
paths_allowed(paste(paths="/en/real-estate/rent/city/", cities, sep=""),
              domain="https://www.immoscout24.ch")
get_robotstxt(domain="https://www.immoscout24.ch")
```
--> Yes 


LOOPING OVER EACH CITY

Getting the URL of each cities in new variables linked to each of them:


```{r}
for (i in 1:length(cities)){
  attr(cities[[i]], which="url") <- paste(
    "https://www.immoscout24.ch/en/real-estate/rent/city-", 
    names(cities[i]), sep="") 
}
```

```{r}
pages <- list()
for( i in 1:length(cities)){
  pages[[i]] <- read_html(x = paste0(unlist(attributes(cities[[i]]), 
                                            use.names = FALSE))) %>%
    html_nodes(css = ".cXTlXt") %>%
    html_text() %>%
    as.numeric() %>%
    max(na.rm = TRUE) %>%
    subtract(e2 = 1) %>%
    seq(from = 1) 
}
```


Scrapping everything at once:
```{r}
for (i in 1:length(cities)){
  for (page in pages[[i]]){  
    url_path_page_immoscout <- cities[[i]] %>% 
      attributes %>% 
      unlist(use.names = FALSE) %>% 
      paste0 %>%
      paste("?pn=", page, sep="") 
    
    cities[[i]][[page]] <- list()
    cities[[i]][[page]] <- read_html(url_path_page_immoscout) %>% 
      html_nodes(".csgoYM") %>%
      html_text()
  }
}
```

Creating one big dataframe with all values of all cities to be used later (not cleaned yet) 
```{r}
unlisted_cities <- unlist(cities) %>% data.frame
```



Iegor's code
```{r}
item_full_info <- read_html(
  "https://www.immoscout24.ch/en/real-estate/rent/city-lausanne?pn=1") %>%
  html_nodes(".csgoYM") %>%
  html_text()
```


Creating a dataframe for each city

Getting only the big dataframe (named all_cities) directly without creating "subdataframes"

```{r}
all_cities <- data.frame()
for (i in 1:length(cities)) {
  item_full_info <- unlisted_cities[grep(names(cities[i]), 
                                         rownames(unlisted_cities)),] 
  #extract number of rooms
  

  assign(paste("df_", names(cities[i]), sep=""),  
         data.frame(
           rooms = str_extract(item_full_info, ".*m\u00B2") %>%
             # first taking before m2 for the cases where the word "room" or "rooms" 
             # is mentionned in the description
             str_extract(., ".*rooms*") %>% 
             gsub(pattern = " rooms", replacement = "", fixed = TRUE) %>%
             gsub(pattern = " room", replacement = "", fixed = TRUE) %>% 
             as.numeric
           ,
           
           # Extract Size
           m2 = str_extract(item_full_info, ".*m\u00B2\u00AB") %>%
             str_extract(., ", .*") %>%
             gsub(pattern=" m\u00B2\u00AB", replacement = "", fixed = TRUE) %>%
             gsub(pattern= ", ", replacement = "", fixed = TRUE) 
           %>% as.integer
           ,
           
           # Extract localiation
           address =  str_extract(item_full_info, ".*Close") %>%
             str_extract(., ".*,") %>%
             str_extract(., "\u00bb.*") %>%
             gsub(pattern = "Close", replacement = "", fixed = TRUE) %>%
             gsub(pattern = ",", replacement = "", fixed = TRUE) %>%
             gsub(pattern = "\u00bb", replacement = "", fixed = TRUE) %>%
             gsub(pattern = "\u00FC", replacement = "u", fixed = TRUE) %>%
             gsub(pattern = "\u00E4", replacement = "a", fixed = TRUE) %>%
             gsub(pattern = "\u00F6", replacement = "o", fixed = TRUE) %>%
             gsub(pattern = "\u00E8", replacement = "e", fixed = TRUE) %>%
             gsub(pattern = "\u00E9", replacement = "e", fixed = TRUE) %>%
             gsub(pattern = "\u00EA", replacement = "e", fixed = TRUE) %>%
             gsub(pattern = "\u00F4", replacement = "o", fixed = TRUE) %>%
             gsub(pattern = "\u00EF", replacement = "i", fixed = TRUE)
           ,
           
           #extract price
           price = str_extract(item_full_info, "eCHF .*") %>% str_extract(., ".*.\u2014 *") %>% 
             gsub(pattern = "eCHF ", replacement = "", fixed = TRUE) %>%
             gsub(pattern = ".\u2014", replacement = "", fixed = TRUE) %>%
             gsub(pattern = ",", replacement = "", fixed = TRUE) %>% as.integer
           ,
           
           # Assign the city
           city = names(cities[i])
         )
         )

  city <-  data.frame(
    rooms = str_extract(item_full_info, ".*\u00AB") %>%
      # first taking before m2 for the cases where the word "room" or "rooms" 
      # is mentionned in the description
      str_extract(., ".*room") %>% 
      gsub(pattern = " room", replacement = "", fixed = TRUE) %>% 
      as.numeric
    ,
    
    # Extract Size
    m2 = str_extract(item_full_info, ".*m\u00B2\u00AB") %>%
      # str_extract(., ", .*") %>%
      gsub(pattern=" m\u00B2\u00AB", replacement = "", fixed = TRUE) %>% 
      word(.,-1) %>% 
      as.integer
    ,
    
    #extract price
    price = str_extract(item_full_info, "eCHF .*") %>% 
      str_extract(., ".*.\u2014 *") %>% 
      gsub(pattern = "eCHF ", replacement = "", fixed = TRUE) %>%
      gsub(pattern = ".\u2014", replacement = "", fixed = TRUE) %>%
      gsub(pattern = ",", replacement = "", fixed = TRUE) %>% 
      as.integer
    ,
    
    # Extract localiation
    address =  str_extract(item_full_info, ".*Close") %>%
      str_extract(., ".*,") %>%
      str_extract(., "\u00bb.*") %>%
      gsub(pattern = "Close", replacement = "", fixed = TRUE) %>%
      gsub(pattern = ",", replacement = "", fixed = TRUE) %>%
      gsub(pattern = "\u00bb", replacement = "", fixed = TRUE) %>%
      gsub(pattern = "\u00FC", replacement = "u", fixed = TRUE) %>%
      gsub(pattern = "\u00E4", replacement = "a", fixed = TRUE) %>%
      gsub(pattern = "\u00F6", replacement = "o", fixed = TRUE) %>%
      gsub(pattern = "\u00E8", replacement = "e", fixed = TRUE) %>%
      gsub(pattern = "\u00E9", replacement = "e", fixed = TRUE) %>%
      gsub(pattern = "\u00EA", replacement = "e", fixed = TRUE) %>%
      gsub(pattern = "\u00F4", replacement = "o", fixed = TRUE) %>%
      gsub(pattern = "\u00EF", replacement = "i", fixed = TRUE) %>%
      gsub(pattern = "\u00EB", replacement = "e", fixed = TRUE) %>%
      gsub(pattern = "\u00EE", replacement = "e", fixed = TRUE) %>%
      gsub(pattern = "\u00E7", replacement = "c", fixed = TRUE) %>%
      gsub(pattern = "\u00E2", replacement = "a", fixed = TRUE) 
    ,
    
    postcode = str_extract(item_full_info, ".*Close") %>%
      str_extract(., ".*,") %>%
      str_extract(., "\u00bb.*") %>%
      gsub(pattern = "Close", replacement = "", fixed = TRUE) %>%
      gsub(pattern = ",", replacement = "", fixed = TRUE) %>% 
      gsub(pattern = "\u00bb", replacement = "", fixed = TRUE)  %>%
      word(., -2),
    
    city = str_extract(item_full_info, ".*Close") %>%
      str_extract(., ".*,") %>%
      str_extract(., "\u00bb.*") %>%
      gsub(pattern = "Close", replacement = "", fixed = TRUE) %>%
      gsub(pattern = ",", replacement = "", fixed = TRUE) %>% 
      gsub(pattern = "\u00bb", replacement = "", fixed = TRUE) %>%
      gsub(pattern = "\u00FC", replacement = "u", fixed = TRUE) %>%
      gsub(pattern = "\u00E8", replacement = "e", fixed = TRUE) %>%
      word(., -1)
  )
  all_cities <- rbind(all_cities, city)
}

# selecting only prices > 500 to get rid off most of wrong recorder data
# and weakly rents
all_cities <- all_cities[all_cities$price > 300,]

# Deleting rows where we have NA (about 16% of the data)
all_cities <- all_cities[complete.cases(all_cities),] 

all_cities <- cbind(all_cities, latitude = NA, longitude = NA)
```

```{r}
all_cities <- readRDS(file = "all_cities.rds")
loz <- all_cities %>% filter(city == "Lausanne")
```


#### Genereting map 

```{r}
# API key obtained with the test period (google)
# set_key("AIzaSyBQd93y1YsbrWKxMgnaRXoX0Wg6F-fiCqc")

# Create a df with raw information about the address coordinates
# raw_coordinates <- google_geocode(address = "Via Monte Carmen 8 6900 Lugano")

# Create a df with only a column lng and a column ltd
# coordinates_df <- raw_coordinates$results$geometry$location

# Using leaflet package to map the coordinates
leaflet(options = leafletOptions(minZoom = 7.4)) %>%
setMaxBounds(6, 47.9, 10.5, 45.8) %>%
addTiles() %>%  # Add default OpenStreetMap map tiles
addMarkers(lng = loz$longitude, lat = loz$latitude, popup = paste("Price:", loz$price))
```

```{r}

# GEOCODING FOR ALL THE ADDRESSES

# for (i in 2911:nrow(all_cities)) {
#   
#   location <- google_geocode(
#     as.vector(all_cities$address[i])
#   )$results$geometry$location
#   
#   if(!is.null(location)) {
#     all_cities[i, "latitude"] <- location$lat[1]
#     all_cities[i, "longitude"] <- location$lng[1]
#     
#   }
# }

# write.csv(all_cities, file = "all_cities.csv")
```

