---
title: "Swiss Real Estate Map <br/> PTDS Project"
author: "Luca Bron, David Germano, Patrik Grandadam, Vincent Lomazzi, Edgar Raisin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: ioslides_presentation
runtime: shiny
---

```{r, include = FALSE}
library(swissimmo)
library(png)
library(grid)
library(googleway)
library(dplyr)
library(kableExtra)
set_key("AIzaSyBQd93y1YsbrWKxMgnaRXoX0Wg6F-fiCqc")
```


# 1. Our project
## 1.1 Objectives

* Create an interactive map of the Swiss real estate market
* Create a R package allowing users to web scrap updated real estate data on Immoscout24
```{r, fig.width = 7, echo = FALSE}
img <- readPNG("Images/MapExample.png")
grid.raster(img)
```

## 1.2 Methodology

* Data web scraping on Immoscout24
* Data cleaning
* Create a data frame with all relevant data
* Geocoding to get longitudes and latitudes for each observation using googleway package
* Use of prediction models to determine predicted prices

# 2. Swissimmo package

## <b>get_immodata2()</b>
Web scrap Immoscout24 data by city and adding coordinates and predicted price
```{r, error = FALSE, message = FALSE, comment = NA, warning = FALSE, results = 'hide'}
cities <- get_immodata2("crissier") 
```

```{r, echo = FALSE}
head(cities, n = 4L) %>% kable()
```


## <b>predict_price()</b>
Create a new "pred" object with the predicted price
```{r, eval = FALSE}
# Predictions based on the cities dataframe
cities_pred <- predict_price(cities)
```

```{r, echo = FALSE}
# Predictions based on the cities dataframe
cities_pred <- predict_price(cities)
```

```{r}
# Predictions based on the following attributes
predict_price(rooms = 3, m2 = 59, city = "nyon")
```

## <b>summary.pred</b>
Extract the price of "pred" object

```{r, eval = FALSE}
summary(cities_pred)
```

```{r, echo = FALSE}
summary(cities_pred) %>% head(n = 4L) %>% kable
```


## <b>plot.pred()</b>
Plot the predictions against the real values of "pred" object
```{r, error = FALSE, message = FALSE, comment = NA, warning = FALSE, results = 'hide'}
plot(cities_pred)
```


# 3. Shiny App
## Demonstration

```{r, echo = FALSE}
all_cities <- readRDS(file = "all_cities.rds") 
```


```{r}
swissmap(all_cities) # 8 biggest cities obtained with the presented methods
```

