---
title: "Swiss Real Estate Map <br/> PTDS Project"
author: "Luca Bron, David Germano, Patrik Grandadam, Vincent Lomazzi, Edgar Raisin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  ioslides_presentation: default

---
```{r, include = FALSE}
library(swissimmo)
library(png)
library(grid)
library(googleway)
set_key("AIzaSyBQd93y1YsbrWKxMgnaRXoX0Wg6F-fiCqc")
```


# 1. Our project
## 1.1 Objectives

* Create an interactive map of the Swiss real estate market
* Create a R package allowing users to web scrap updated real estate data on Immoscout24
```{r, fig.width = 7, echo = FALSE}
img <- readPNG("Images/MapExample.png")
grid.raster(img)
```

## 1.2 Methodology

* Data web scraping on Immoscout24
* Data cleaning
* Create a data frame with all relevant data
* Geocoding to get longitudes and latitudes for each observation using googleway package
* Use of prediction models to determine predicted prices

# 2. Swissimmo package

## <b>get_immodata2()</b>
Web scrap Immoscout24 data by city and adding coordinates and predicted price
```{r}
# cities <- get_immodata("crissier")
#head(cities)
```
## <b>my_theme()</b>
Theme for ggplot graphs

## <b>plot.pred()</b>
Plot the predictions against the real values

## <b>predict_price()</b>
Create a new "pred" object with the predicted price
```{r}
#Predictions based on the cities dataframe
# predict_price(cities)
```

```{r}
#Predictions based on the following attributes
# predict_price(rooms = 3, m2 = 59, city = "nyon")
```

## <b>summary.pred</b>
Extract the price of "pred" object

# 3. Shiny App
## Demonstration
